A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-02-23 analysis/paper.Rmd
update
edit based on comments

initial_populations<- c(7500,15000,22500)
#initial_populations<- c(100,150,225)
years <- c(1906:2010)
#years <- c(1906:1966)
ages <- c(0:120)
#ages <- c(0:75)

@@

    # Save simulation results
    #save(meta.res1,file=file.path(paste0("./results/models"),paste("models",sprintf(file_number_format,pset),".Rdata",sep="")))

    save(results,file=file.path(paste0("./results/models/p",ip),paste("models",sprintf(file_number_format,pset),".Rdata",sep="")))
  }

>>>>

initial_populations<- c(7500,15000,22500)
years <- c(1906:2010)
ages <- c(0:120)

@@

    # Save simulation results
    save(results,file=file.path(paste0("./results/models/p",ip),paste("models",sprintf(file_number_format,pset),".Rdata",sep="")))
  }
